Graphics

### 2020-06-02 individual-cohorts/graphics_t_statistics.Rmd
fix df

```{r functions}
plot_t <- function(df, conditions){
  p = list()
  for(i in seq_along(conditions[,1])){
  positions = conditions[i,]
  positions
  x = df[positions[1]]
  y = df[positions[2]]
  computed_cor = cor(x, y, method = "spearman")
  x_var <- names(x)
  y_var <- names(y)
  p[[i]] = ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_hex() +
  geom_abline() +
  theme_bw() +
  labs(
    caption = paste0("spearman correlation between the statistics is ", round(computed_cor, digits = 3))
  ) +
    theme(aspect.ratio=1)
  }
multiplot(plotlist = p, cols = 2)
}
```

# Control vs Other
```{r plota, fig.width = 20, fig.height = 40}
df_one <- df[df$Comparison %in% "Control_vs_Other",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

@@

# Control vs SCZ
```{r plotb, fig.width = 20, fig.height = 40}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

@@

# Other vs SCZ
```{r plotc, fig.width = 20, fig.height = 40}
df_three <- df[df$Comparison %in% "Other_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.)))

>>>>

```{r functions}
plot_t <- function(df, conditions){
  p = list()
  for(i in seq_along(conditions[,1])){
  positions = conditions[i,]
  x = df[positions[1]]
  y = df[positions[2]]
  computed_cor = cor(x, y, method = "spearman")
  x_var <- names(x)
  y_var <- names(y)
  p[[i]] = ggplot(df, aes(x = .data[[x_var]], y = .data[[y_var]])) +
  geom_hex() +
  geom_abline() +
  theme_bw() +
  labs(
    caption = paste0("spearman correlation between the statistics is ", round(computed_cor, digits = 3))
  ) +
    theme(aspect.ratio=1)
  }
multiplot(plotlist = p, cols = 2)
}
```

# Control vs Other
```{r plota, fig.width = 20, fig.height = 40}
df_one <- df[df$Comparison %in% "Control_vs_Other",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.))) %>% 
  dplyr::select(-Comparison)

@@

# Control vs SCZ
```{r plotb, fig.width = 20, fig.height = 40}
df_two <- df[df$Comparison %in% "Control_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.))) %>% 
  dplyr::select(-Comparison)

@@

# Other vs SCZ
```{r plotc, fig.width = 20, fig.height = 40}
df_three <- df[df$Comparison %in% "Other_vs_SCZ",] %>% 
  group_by(gene_id) %>% 
  dplyr::filter(row_number()==1) %>% 
  tibble::column_to_rownames(var = "gene_id") %>% 
  dplyr::select_if( ~ !all(is.na(.))) %>% 
  dplyr::select(-Comparison)
